### 2018-09-08 Sections/network_algorithms.tex
minor

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ConstrainedShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item For the set of nearest-neighbour constraints, generate the set of edges $E_c$ that violate the constraints.
	\item $G'=G-E_c$
	\item route = DijkstraShortestPath($G'$,$A$,$B$)
	\item return(route)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Efficient algorithm for finding a constrained shortest-path, where the constraints are in terms of nearest-neighbour relationships.} \label{alg:const_short}\index{Constrained shortest-path algorithm}
\end{table}

@@

A notable example of where this technique finds applicability is in entanglement swapping networks, discussed later in Secs.~\ref{sec:swapping} \& \ref{sec:rep_net}. Consider the network shown in Fig.~\ref{fig:racetime}. Here the entanglement swapping network comprises nodes alternating between two different functionalities: Bell-pair preparation, and entanglement swapping. Representing these as colours, this effectively introduces the edge constraint that edges between nearest neighbours of the same colour ought to be removed. Additionally, the end-points of the network must neighbour Bell-pair sources, not entanglement swappers. This enforces the additional constraint of removing edges between end-points with the wrong coloured neighbours. Having applies these edge deletions enforcing these constraints, the shortest-path algorithm will now find the constrained optimal route. Thus, this example of entanglement swapping network is isomorphic to the example presented in Fig.~\ref{fig:constrained_shortest_path}.

>>>>

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ConstrainedShortestPath($G$,$A$,$B$,$C$):
\begin{enumerate}
	\item For the set of nearest-neighbour constraints $C$, generate the set of edges $E(C)$ that violate the constraints.
	\item $G'=G-E(C)$
	\item route = DijkstraShortestPath($G'$,$A$,$B$)
	\item return(route)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Efficient algorithm for finding a constrained shortest-path, where the constraints are in terms of nearest-neighbour relationships.} \label{alg:const_short}\index{Constrained shortest-path algorithm}
\end{table}

@@

A notable example of where this technique finds applicability is in entanglement swapping networks, discussed later in Secs.~\ref{sec:swapping} \& \ref{sec:rep_net}. Consider the network shown in Fig.~\ref{fig:racetime}. Here the entanglement swapping network comprises nodes alternating between two different functionalities: Bell-pair preparation, and entanglement swapping. Representing these as colours, this effectively introduces the edge constraint that edges between nearest neighbours of the same colour ought to be removed. Additionally, the end-points of the network must neighbour Bell-pair sources, not entanglement swappers. This enforces the additional constraint of removing edges between end-points with the wrong coloured neighbours. Having applies these edge deletions enforcing these constraints, the shortest-path algorithm will now find the constrained optimal route. Thus, this example of an entanglement swapping network is isomorphic to the example presented in Fig.~\ref{fig:constrained_shortest_path}.
